preprocessing

### 2022-11-14 r-prep/prep.Rmd
prep

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  left_join(data_lulucf,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(
    EU = case_when(country %in% eurostat::eu_countries[2]$name~ TRUE, TRUE ~ FALSE),

  )

>>>>

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  left_join(data_lulucf,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(
    EU = country %in% eurostat::eu_countries[2]$name,
    woc = country != "China",
    deving_woc = woc & data_base$region_ar6_dev == "developing",
    deved = data_base$region_ar6_dev == "developed",
    adp_region_woc = woc & data_base$region_ar6_6 == "Asia and developing Pacific",
    adp_region_deving_woc = adp_region_woc & deving_woc
  ) %>% 
  select(-woc)
